### 2017-05-24 gpu-04-03-accelerator.tex
Move remark on 32-bit to sequential

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Single floating point vs double
Another modification to the original algorithm is migrating all of its
computation from double to single precision floating-point.
%
This change affects the algorithm in multiple ways. For instance, it reduces
both the computation and data intensity. It again reduces the memory
footprint of the algorithm and frees registers, enabling more
effective data reuse.
%
It has been previously shown that stochastic learning algorithms do not require
high precision in the presence of statistical approximations and the addition
of random noise~\cite{DBLP:journals/corr/GuptaAGN15}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Single floating point vs double
Another modification to the original algorithm is migrating all of its
computation from double to single precision floating-point, analogous to the change
for the baseline implementation in Section~\ref{sec-seq-performance}.
%
This change affects the algorithm in multiple ways. For instance, on a GPU it reduces
both the computation and data intensity. It again reduces the memory
footprint of the algorithm and frees registers.
